17th International Satisfiability Modulo Theories Competition (SMT-COMP 2022): Rules and Procedures

### 2022-04-08 rules/rules22.tex
addressing todos

  \item {\bf \prooftrack.}  \todo{after we iron it out.}

@@

The output of the solver is then fed to a proof checker, which also
needs be provided by the solver authors.  The input to the proof
checker is the whole output of the solver including the \texttt{unsat}
reply to the \akey{check-sat} command.  The proof checker should
output either \texttt{valid} or \texttt{invalid} to indicate that the
proof was valid.  \todo{Further statistics?}

@@

\header{New benchmarks.}
The deadline for submission of new benchmarks was {\bf March~15, 2021}
\hb{update when we have date}.
%
The organizers, in collaboration with the SMT-LIB maintainers, will be
checking and curating these until {\bf June~18, 2022}.

@@

\item \todo{excluding and including benchmarks based on statuses and runs}
  For the \prooftrack and \ucoretrack, all benchmark with status
  \texttt{sat} are removed.  We further remove benchmarks with status
  \texttt{unknown} for which no solver reported them to be
  \texttt{unsat}.
  %
  For the \mvaltrack,  all benchmark with status \texttt{unsat} are removed,
  as well as benchmarks with status
  \texttt{unknown} for which no solver reported them to be
  \texttt{sat}.

@@

\header{Disclosure.}
%
Haniel Barbosa is part of the developing teams of the SMT solvers
cvc5~\cite{cvc4-smtcomp18} \hb{update reference} and veriT~\cite{verit}.
%
Fran\c{c}ois is part of the developing team of the SMT solver COLIBRI~\cite{colibri}.
%
Jochen Hoenicke is part of the developing team of the SMT solver
SMTInterpol~\cite{smtinterpol}.

>>>>

  \item {\bf \prooftrack.}  This track will be introduced this year.
  %
  Teams can submit proof-producing solvers together with proof checkers for
  their proof formats. The checker and format do not need to be from the same
  team as the solver.
  %
  We will compile and present the results, as well as assemble a panel of
  non-organizer experts to do a qualitative assessment for each proof-producing
  solver, proof format, and proof checker.
  %
  The solver, proof format and checker should be described in a system
  description (total of 4 pages rather than 2).

  \rationale{Given the many competing visions on how SMT proofs or a proof
    competition should look like, we decided to be less prescriptive and more
    descriptive for how SMT-COMP will approach proofs.
    %
    We will host a ``proof exhibition'' rather than a ``proof competition''
    track. The format would be with teams submitting both a proof-producing SMT
    solver and a proof checker for its proofs.
 }

@@

The output of the solver is then fed to a proof checker, which also needs to be
provided by the solver authors (but it does not need to authored by them).
%
The input to the proof checker is the whole output of the solver including the
\texttt{unsat} reply to the \akey{check-sat} command.
%
The proof checker's output should start with a line containing either
\texttt{valid} or \texttt{invalid} to indicate that the proof was valid.
%
The rest of the output can be arbitrary (for example the proof checker may print
out statistics).

@@

\header{New benchmarks.}
The deadline for submission of new benchmarks was {\bf March~15, 2021}.
%
The organizers, in collaboration with the SMT-LIB maintainers, will be
checking and curating these until {\bf June~18, 2022}.

@@

\item
  For the \prooftrack and \ucoretrack, all benchmarks with status
  \texttt{sat} are removed.  We further remove benchmarks with status
  \texttt{unknown} for which no sound solver reported them to be
  \texttt{unsat}.
  %
  For the \mvaltrack,  all benchmarks with status \texttt{unsat} are removed,
  as well as benchmarks with status
  \texttt{unknown} for which no sound solver reported them to be
  \texttt{sat}.

@@

\header{Disclosure.}
%
Haniel Barbosa is part of the developing teams of the SMT solvers
cvc5~\cite{cvc5} and veriT~\cite{verit}.
%
Fran\c{c}ois is part of the developing team of the SMT solver COLIBRI~\cite{colibri}.
%
Jochen Hoenicke is part of the developing team of the SMT solver
SMTInterpol~\cite{smtinterpol}.
